Differentially Private Bayesian Inference

### 2018-04-13 main.tex
uodate efficiency

\section{Bayesian Inference Based on Beta-Bernoulli Distribution}
\label{sec_bayesInfer}

\section{Algorithm Setting up}
\label{sec_setup}
The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\bysinfer(x)$.

@@

\section{Experimental Evaluations}
\subsection{Computation Efficiency}
The formula to compute the local sensitivity is presented in Sec. \ref{subsec_emls}.

>>>>

\section{Bayesian Inference Based on Beta-Bernoulli Distribution}
\label{sec_bayesInfer}
The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\bysinfer(x)$.

\section{Algorithm Setting up}
\label{sec_setup}

@@

\section{Experimental Evaluations}
\subsection{Computation Efficiency}
The formula for computing the local sensitivity is presented in Sec. \ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hlg(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property. i.e., the maximum value over $\max\limits_{r \in R}$ always happen when $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(x), \bysinfer(x)) - \hlg(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(y'), \bysinfer(x))|\}$. We also have some experiments for validating our proposal as in Fig. \ref{fig_efficiency}, where we calculate the $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$. It is shown that maximum value taken when  $r = \bysinfer(x)$.

 \begin{figure}[h]
    \centering
    \includegraphics[width=1.0\textwidth]{efficiency}
    \label{fig_efficiency}
    \caption{An Experimental Result for Finding the Local Sensitivity efficiently}
    \end{figure}
\subsection{}
